---
output: github_document
---

```{r echo=FALSE, results = 'asis'}
pkg <- 'pomdpSolve'

source("https://raw.githubusercontent.com/mhahsler/pkg_helpers/main/pkg_helpers.R")
pkg_title(pkg)
```

Provides [pomdp-solve](http://www.pomdp.org/code/) (Cassandra, 2015) to solve POMDPs using
a variety of algorithms.
A convenient interface is provided in package [pomdp](https://github.com/mhahsler/pomdp). 

```{r echo=FALSE, results = 'asis'}
pkg_install(pkg)
```

## Usage

Solve a POMDP file that ships with this package in a temporary directory and read the solution.
```{r }
library(pomdpSolve)

old_wd <- setwd(tempdir())
file.copy(system.file("tiger.aaai.POMDP", package = "pomdpSolve"), "./tiger.aaai.POMDP")

pomdp_solve("tiger.aaai.POMDP", options = list(method = "grid"), verbose = FALSE)
dir()

read_alpha_file("tiger.aaai-0.alpha")
read_pg_file("tiger.aaai-0.pg")

setwd(old_wd)
```

The value function is defined by a set of alpha vectors represented as $V$ components rows in a matrix. Each alpha vector corresponds to 
a node with the same row number in the policy graph. The policy graph represents the policy in the form of a data.frame with one row for each node. Nodes have a node id $N$, the action $A$ defined by the policy and then for each observation $Z$ the id (row) of the policy graph node to transition to.

A detailed description of the available solver options can be found [here](https://mhahsler.github.io/pomdpSolve/pomdp-solve_manual).

## How to Cite this Package
```{r echo=FALSE, results = 'asis'}
citation(pkg)
```

## References

* Cassandra, A. (2015). pomdp-solve: POMDP Solver Software, http://www.pomdp.org.

